Fixing Lost JavaScript Function Names in Debuggers

### 2011-03-30 papers/splash-wavefront2011/sigplanconf-template.tex

\section{Automated Funcation Naming}
%	We instead, to tackle the aforementioned issues caused due to the lack of function names, propose automated function naming by anlyzing the source code. Before getting into details of how the function name is constructed, we discuss the rationale behind some of decisions we made in this approach.
  Developers usually understand and refer to function objects by aliases they use to access them. This fact particularly holds for permanent function objects such as classes and utility functions. However, functions with shorter lifetimes such as closures and callbacks are referred by their roles or purposes in the program. We employ these facts to construct an identifier for a function. We analyse the source code to locate alias(es) which the function object is assigned to. If the list of aliases is not empty we select the most appropriate one based on some ranking rules as the function name. Otherwise, we try to build a name based on the aliases that the function object somehow affect on their values. If there is no such alias then the function object is consumed as an argument in a chain of function calls that does not return any value or as a simple closure. If the case of function calls chain we use the most nested called function name for constructing the identifier. In the case of simple closure, we employ the function(s) identifier inside the closure to construct the identifier.

@@

   To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}. We can recognize seven function bodies in the code, none of them has a name. For every function we first build a summary. The summary explains how the function object is used in relation to other identifiers. The first function defined in line 9 is called just after its creation and returns another function defined in line 10. The result is assigned to variable {\small\texttt{main}}. In this case the summary for the first function is {\small\texttt{main<}} as it produces the {\small\texttt{main}} object. The second function is directly assigned to {\small\texttt{main}} and thus its name will be {\small\texttt{main}}.

%    Therefore the internal function body is named {\small\texttt{main<}} as its corresponding function object is assinged to a variable with this name. What about the outer function itself? We name that {\small\texttt{mainClosure}}, as it is used as a closure for the returned function.

The third function (defined in line 14), is passed as an argument to another function with name {\small\texttt{op}}. This function contributes in producing the {\small\texttt{result}} value. Therefore, the summary will be {\small\texttt{main</return/result<}} and the function is named as {\small\texttt{main</result<}}.
%We may name the function {\small\texttt{op(1)}}, as it is passed as the first argument to {\small\texttt{op}}). A better choice instead of the argument index would be the the argument name in the called function (here {\small\texttt{op(callback)}}). However the latter requires knowning the function body of the called function which is not always possible.

As we explained in the previous section, {\small\texttt{FOO}} and {\small\texttt{BAR}} are good name candidates for functions defined in lines 19 and 22, as these functions are directly assigned to variable with the same names. The functions in lines 25 and 27 are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.

>>>>

\section{Automated Funcation Naming}
%	We instead, to tackle the aforementioned issues caused due to the lack of function names, propose automated function naming by anlyzing the source code. Before getting into details of how the function name is constructed, we discuss the rationale behind some of decisions we made in this approach.
  Developers usually understand and refer to function objects by aliases they use to access them. This fact particularly holds for permanent function objects such as classes and utility functions. However, functions with shorter lifetimes such as closures and callbacks are referred by their roles or purposes in the program. We employ these facts to construct an identifier for a function. We analyse the source code to locate alias(es) which the function object is assigned to. If the list of aliases is not empty we select the most appropriate one based on some ranking rules as the function name. Otherwise, we try to build a name based on the aliases that the function object somehow affect on their values. If there is no such alias then the function object is consumed as an argument in a chain of function calls that does not return any value or as a simple closure. In the case of function calls chain we use the most nested called function name for constructing the identifier. In the case of simple closure, we employ the function(s) identifier inside the closure to construct the identifier.

@@

   To illustrate the basic idea, we use the JavaScript code presented in Figure~\ref{js-code}. We can recognize seven function bodies in the code, none of them has a name. The first function in line 9 is called just after its creation and sets the {\small\texttt{main<}} value. We name this function {\small\texttt{main<}}. The symbol {\small\texttt{<}} shows that the function object contributes to the {\small\texttt{main}} value. To name the function object defined in line 10, we analyze the code to get the aliases used for the function object after its creation. Once the function object is created it is returned. As the enclosed function is just called after its creation we can continue our search for more aliases in the outer scope. The function object is assigned to {\small\texttt{main}}. Therfore we name it {\small\texttt{main}}.

   %For every function we first build a summary. The summary explains how the function object is used in relation to other identifiers. The first function defined in line 9 is called just after its creation and returns another function defined in line 10. The result is assigned to variable {\small\texttt{main}}. In this case the summary for the first function is {\small\texttt{main<}} as it produces the {\small\texttt{main}} object. The second function is directly assigned to {\small\texttt{main}} and thus its name will be {\small\texttt{main}}.
%    Therefore the internal function body is named {\small\texttt{main<}} as its corresponding function object is assinged to a variable with this name. What about the outer function itself? We name that {\small\texttt{mainClosure}}, as it is used as a closure for the returned function.

The third function (defined in line 14), is passed as an argument to another function with name {\small\texttt{op}}. This function contributes in producing the {\small\texttt{result}} value. Moreover, it is located inside another function which is named {\small\texttt{main<}}. Therefore, its full name will be {\small\texttt{main</result<}}. The symbol {\small\texttt{/}} is used to separate the context name from the function name.

%Therefore, the summary will be {\small\texttt{main</return/result<}} and the function is named as {\small\texttt{main</result<}}.
%We may name the function {\small\texttt{op(1)}}, as it is passed as the first argument to {\small\texttt{op}}). A better choice instead of the argument index would be the the argument name in the called function (here {\small\texttt{op(callback)}}). However the latter requires knowning the function body of the called function which is not always possible.

The functions defined in lines 19 and 22, are directly assigned to {\small\texttt{FOO}} and {\small\texttt{BAR}}. Therefore, the same names will be used for the functions. The last two functions defined in lines 25 and 27, similar to functions in lines 9 and 10, are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.

%As we explained in the previous section, {\small\texttt{FOO}} and {\small\texttt{BAR}} are good name candidates for functions defined in lines 19 and 22, as these functions are directly assigned to variable with the same names. The functions in lines 25 and 27 are named {\small\texttt{op<}} and {\small\texttt{op}} respectively.
